On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-23 paper.tex
update 11/23 in Tokyo

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%l.168 - 1324

@@

@@

\begin{paragraph}{Case of obtuse}
\begin{itemize}
\item[-] Case of $n_3$ is free\\
Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
\item[-] Case of $n_4$ is free\\
%n4??????????lemma2??n2???????lemma???n0??????????????w[i]???????????????????????bead?????????????1?????
%??n0?????????????n3???????????lemma1??n-3????????n-3???????????n-2??????????n-1???????????????w[i]???????????????????w[i]????????????
%??n3?????????????n0????????????lemma1??n-1???????????n-2?n-3???????w[i]?????????????
%???n0 n3???beead???????????n0 n3 ????????????lemma1??n-1 n-3????????n-1,n-3????????????n-3???????????
%???n-4????????????in order to provide inifinite structures?
\item[-] Case of $n_2$ is free\\
Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied. Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_2$ has to be occupied.
\item[-] Case of $n_0$ is free\\
Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied. Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_0$ has to be occupied. 
\end{itemize}

@@

%end of d = 1
%//////////////////////////////////////////////////////% l.168 - 1324
%//////////////////////////////////////////////////////%

>>>>

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%l.168 - 1326

@@

\subsubsection{$\alpha = 2$}

@@

\begin{paragraph}{Case of obtuse}
\begin{itemize}
\item[-] Case of $n_3$ is free\\
Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
\item[-] Case of $n_4$ is free\\
According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free. Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}. Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied. Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied. In the same previous way, any $n_{-2}, n_{-3}$ are occupied.  Therefore any neighbors of $w[i]$ are occupied.\\
If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied. If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied. If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
Thus $n_3$ has to be occupied in order to yield infinite structures.
\item[-] Case of $n_2$ is free\\
Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied. Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_2$ has to be occupied.
\item[-] Case of $n_0$ is free\\
Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied. Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_0$ has to be occupied. 
\end{itemize}

@@

%end of d = 1
%//////////////////////////////////////////////////////% l.168 - 1326
%//////////////////////////////////////////////////////%
